Unifying Gompertzian growth with the communicable disease spreading paradigm

### 2022-04-25 main.tex
add refs

\subsection{Unification through a modified SIR model}
However, it is possible to reconcile the SIR model with the Gompertz curve from yet another argument. 
Inspired by the observation that in the linearized approximation there are only two coupled states, infected and susceptible, we augment the interaction term to higher orders. 
Then, we reverse the causality where the population of infected are now dependent of the population of the susceptible instead of the other way around as in (\ref{eq:networkSIR}),
\begin{equation}
\label{eq:reverseNetworkSIR}
\frac{d f_i}{dt} = \beta f_i\sum_j{a_{ij}}(1-f_j) \quad \forall i.
\end{equation} 
This crucial change is based on the environmental stressor hypothesis rather than a communicable disease assumption.
Furthermore, we will for the sake of simplicity assume all nodes in the network have exactly one neighbor and that there exists a unique path between all nodes,
\begin{equation}
\sum_i a_{ij} = 1 \quad \forall j.
\end{equation} 
If we let $s_i = 1 - f_i$ be the probability of being susceptible, the augmented and causality-reversed SIR model becomes 
\begin{equation}
\frac{d f_i}{dt} = \beta f_i\sum_j{a_{ij}}(s_{j} + s^2_j/2 + ...) - \alpha f_i\quad \forall i,
\end{equation}

@@

\end{table}
\bibliographystyle{plainnat}
\bibliography{../references2}  %%% Uncomment this line and comment out the ``thebibliography'' section below to use the external .bib file (using bibtex) .

>>>>

\subsection{Unification through a modified SIR model}
However, it is possible to reconcile the SIR model with the Gompertz curve from yet another argument. 
Inspired by the observation that in the linearized approximation there are only two coupled states, infected and susceptible, we augment the interaction term to higher orders. 
Then, we reverse the causality where the population of infected are now dependent of the population of the susceptible instead of the other way around as in (\ref{eq:networkSIR}),
\begin{equation}
\label{eq:reverseNetworkSIR}
\frac{d f_i}{dt} = \beta f_i\sum_j{a_{ij}}(1-f_j) \quad \forall i.
\end{equation} 
This crucial change is based on the environmental stressor hypothesis rather than a communicable disease assumption.
Furthermore, we will for the sake of simplicity assume all nodes in the network have exactly one neighbor and that there exists a unique path between all nodes,
\begin{equation}
\sum_i a_{ij} = 1 \quad \forall j.
\end{equation} 
If we let $s_i = 1 - f_i$ be the probability of being susceptible, the augmented and causality-reversed SIR model infection term becomes 
\begin{equation}
\frac{d f_i}{dt} = \beta f_i\sum_j{a_{ij}}(s_{j} + s^2_j/2 + ...) - \alpha f_i\quad \forall i,
\end{equation}

@@

\end{table}
\bibliographystyle{plainnat}
\bibliography{references2}  %%% Uncomment this line and comment out the ``thebibliography'' section below to use the external .bib file (using bibtex) .
